### 2023-08-11 chapters/background.tex
Some work on the background

In the general public, the concept of uncertainty goes by many names and its meaning can be dependent on a specific context. However, in most quantitative scientific fields, there seems to be a consensus definition along the lines of the following \cite{hubbard_how_2014}:

@@

While a definition of uncertainty made using only words easily begs philosophical inquisition, information theory provides a rigourous method for quantifying uncertainty \cite{kabir_neural_2018} by the language of probabilities. 
In this context, uncertainty is understood as the information entropy of a random variable \cite{mackay_information_2003}.

\subsection{Information entropy}
First characterised by Claude Shannon in 1948 \cite{shannon_mathematical_1948}, information entropy $H(X)$ is a measure of the average amount of information contained in a random variable $X$. Shannon's definition follows from three fundamental axioms of information theory. Let $I_X(x)$ be the information carried by a specific outcome $x$ when sampling the random variable $X$ with probability mass function $p_X(x)$. Then, the axioms are as follows:
\begin{enumerate}
    \item  $I_X(x)$ is a monotonically decreasing function in $p_X(x)$. The more likely an outcome is, the less information it carries.
    \item Outcomes that are certain to happen carry no information. $I_X(1) = 0$.
    \item If an outcome $x_i$ is independent of another outcome $x_j$, then $I(x_i x_j) = I(x_i) + I(x_j)$. The information carried by independent events is the sum of the information carried by each event.
\end{enumerate}

From these axioms, Shannon derived the following expression for the information content of an event $x$ with probability $p_X(x)$:
\begin{equation}
    I_X(x) = -\log_b p_X(x)
\end{equation}

information entropy of a random variable $X$ with $n$ possible outcomes:
\begin{equation}
    H(X) = -\sum_{i=1}^n p_i \log p_i
\end{equation}

>>>>

To the general public, the concept of uncertainty goes by many names, and its meaning can vary depending on the specific context. However, across most quantitative scientific fields, a consensus definition appears to align with the following \cite{hubbard_how_2014}:

@@

While a purely lexical definition of uncertainty might trigger a philosophical inquisition, information theory provides a mathematically rigorous method for quantifying uncertainty through the language of probabilities. 
In this context, uncertainty is understood as the information entropy of a random variable \cite{mackay_information_2003}.

\subsection{Information entropy}
First characterised by Claude Shannon in 1948 \cite{shannon_mathematical_1948}, information entropy, $H(X)$, is a measure of the average amount of information contained in a discrete random variable $X$. Shannon's definition follows from three fundamental axioms of information theory. Let $I_X(x)$ be the information carried by a specific outcome $x$ of sampling the random variable $X$ with probability mass function $p_X(x)$. Then, these axioms are as follows:
\begin{enumerate}[label=(\Roman*)]
    \item The more likely an outcome is, the less information it carries; $I_X(x)$ is a monotonically decreasing function in $p_X(x)$.
    \item Outcomes that are certain to happen carry no information; $I_X(1) = 0$.
    \item The total information carried by independent outcomes is the sum of the information carried by each outcome; $I(x_i, x_j) = I(x_i) + I(x_j)$ if $x_i$ and $x_j$ are independent. 
\end{enumerate}

From these axioms, Shannon found that a suitable function for the \emph{information content} of an outcome $x$ with probability $p_X(x)$ is the logarithm of the inverse probability,
%
\begin{equation}
    I_X(x) = -\log_b p_X(x) \enspace .
\end{equation}
%
Information content is said to be measured in units of bits when using a logarithm with base $b=2$, or nats if $b=e$.

To illustrate the \dots \lesstodo[inline]{Come up with a suitable example explaining the intuition behind information entropy.}

The information entropy of a random variable $X$ is defined as the \emph{expected information content} of an outcome of $X$,
%
\begin{equation}
    H(X) = \mathbb{E}_X\left[I_X(x)\right] = - \sum_{x\in X} p_X(x) \log p_X(x) \enspace .
\end{equation}
%
Intuitively, the entropy $H(X)$ of a discrete random variable $X$ is a measure of the amount of uncertainty associated with the value of $X$ when only its distribution is known. \todo{Rewrite}

\subsection{Continuous entropy}
\lesstodo[inline]{Discuss differential entropy as a generalization to continuous case.}
% Other important information theoretic quantities include Rényi entropy (a generalization of entropy), differential entropy (a generalization of quantities of information to continuous distributions), and the conditional mutual information.

% \cite{kabir_neural_2018} Survey of uncertainty quantification in deep learning.

### 2023-08-11 chapters/conclusion.tex
Make project run in VS Code
Sync-up
Add review paper (WIP)
Add page estimate to conclusion
Some work on the background

%!TEX root = ../Thesis.tex
\chapter{Conclusion}
A conclusion with some citations \cite{kingma_auto-encoding_2014,rezende_stochastic_2014}.

>>>>

%!TEX root = ../thesis.tex

\chapter[conclusions and outlook]{Conclusions and outlook}\label{chp:conclusion}

% ~3 pages

A conclusion with some abbreviations and citations, \gls{VAE} \cite{kingma_autoencoding_2014,rezende_stochastic_2014}.

\lesstodo[inline]{Are self-supervised speech representations useful for unsupervised uncertainty estimation?}

### 2023-08-11 chapters/introduction.tex
Some work on the background

Uncertainty is a fundamental part of human experience. Understanding and quantifying uncertainty is crucial in making informed decisions, drawing meaningful conclusions, and assessing the reliability of predictions made from observations. Yet, capturing it in a mathematical model is a difficult task.

Uncertainty estimation has been a central topic in the field of statistics. It has traditionally been addressed through methods like confidence intervals, hypothesis testing, and Bayesian inference. Confidence intervals provide a range of plausible values for a parameter, while hypothesis testing evaluates the significance of differences between groups or variables \cite{blitzstein_introduction_2019}. Bayesian inference, on the other hand, offers a powerful framework to incorporate prior knowledge and update beliefs based on observed data using probability theory. These approaches have been extensively studied and applied in various domains, from social sciences to natural sciences, to improve the robustness and generalizability of statistical analyses \cite{gelman_bayesian_2013}. However, the widespread adoption in diverse applications of machine learning, and in particular deep neural networks, has posed new challenges in dealing with uncertainty.

@@

Speech processing is

@@

The research in this thesis covers a number of different modelling approaches and tasks, including

The research done over the course of the project at hand covers a varied set of topics. One group of the produced studies is concerned with generative latent variable models and their applications to uncertainty estimation and speech modelling \cite{havtorn_hierarchical_2021,havtorn_benchmarking_2022,bergamin_modelagnostic_2022}. Another group of studies are concerned with self-supervised speech representation learning and automatic speech recognition \cite{borgholt_scaling_2021,borgholt_we_2021,mohamed_selfsupervised_2022,borgholt_brief_2022}. A final group deals with applications within the medical domain including recognition of stroke cases in calls to medical helplines \cite{wenstrup_retrospective_2023} and medical coding of clinical notes \cite{edin_automated_2023}.

>>>>

Uncertainty is a fundamental part of human experience. The ability to understand and quantify uncertainty is crucial in making informed decisions, drawing meaningful conclusions, and assessing the reliability of predictions made from observations. Yet, capturing this ability in a mathematical model is a difficult task.

Uncertainty estimation has long been a central topic in the field of statistics. It has traditionally been addressed through methods like confidence intervals, hypothesis testing, and Bayesian inference. Confidence intervals provide a range of plausible values for a parameter, while hypothesis testing evaluates the significance of differences between groups or variables \cite{blitzstein_introduction_2019}. Bayesian inference, on the other hand, offers a powerful framework to incorporate prior knowledge and update beliefs based on observed data using probability theory. These approaches have been extensively studied and applied in various domains, from social sciences to natural sciences, to improve the robustness and generalizability of statistical analyses \cite{gelman_bayesian_2013}. However, the widespread adoption in diverse applications of machine learning, and in particular deep neural networks, has posed new challenges in dealing with uncertainty.

@@

@@

The research done during this project covers a varied set of topics. One group of the produced studies is concerned with generative latent variable models and their applications to uncertainty estimation and speech modelling \cite{havtorn_hierarchical_2021,havtorn_benchmarking_2022,bergamin_modelagnostic_2022}. Another group of studies are concerned with self-supervised speech representation learning and automatic speech recognition \cite{borgholt_scaling_2021,borgholt_we_2021,mohamed_selfsupervised_2022,borgholt_brief_2022}. A final group deals with applications within the medical domain including recognition of stroke cases in calls to medical helplines \cite{wenstrup_retrospective_2023} and medical coding of clinical notes \cite{edin_automated_2023}.
